\mytitile\\~

### 2019-10-04 document.tex
CRLF to LF
Main picture updated, introduction started

\usepackage{graphicx}% Include figure files
%\usepackage{dcolumn}% Align table columns on decimal point

%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{xparse}
\usepackage{bbm}
\usepackage{hyperref}
%\usepackage{multirow}
%\usepackage{makecell}
\graphicspath{{Pictures/}}

@@

\newcommand{\mytitile}{Effects of intense light-matter interaction in a superconducting artificial molecule}
\begin{document}
	\preprint{AIP/123-QED}

@@

	\maketitle
\section{Introduction}
Over the past twenty years, many

A quantum system exposed to external driving, can experience a number of quantum phenomena due to the resonant transitions between energy levels. The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (AT) splitting\cite{autler1955stark} which can happen in systems with just three energy levels. 
The main attention in our work is paid to the last effect, which related to the dressed states.
The AT effect has been studied in atomic\cite{picque1976direct} and molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and superconducting qubits\cite{li2011decoherence, novikov2013autler}.

>>>>

\usepackage{graphicx}% Include figure files
%\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{fixme}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{xparse}
\usepackage{bbm}
\usepackage{hyperref}
%\usepackage{multirow}
%\usepackage{makecell}
\graphicspath{{Pictures/}}

@@

\newcommand{\mytitile}{Effects of strong interaction between light and matter in a superconducting artificial molecule}
\begin{document}
	\preprint{AIP/123-QED}

@@

	\maketitle
\section{Introduction}
Over the past twenty years, superconducting artificial atoms (SAA) were used in numerous experiments confidently demonstrating the validity of fundamental quantum mechanical laws\cite{you2011atomic}. Due to their synthetic nature, their Hamiltonians can be pre-designed and engineered which makes them a particularly versatile tool for studies in quantum optics. Notably, their parameters may be varied in such a wide range that novel physical effects previously inaccessible for natural systems may be directly observed. For example, the strong coupling regime when the coupling strength between light and a quantum system approaches 1\% of their frequency has been a major milestone for atoms, molecules, etc and was only reached using high-finesse cavities. In contrast, superconducting quantum systems have rapidly attained this landmark using \textit{circuit QED}\cite{wallraff2004strong} just in a few years after their first discovery\cite{chiorescu2004coherent} and have already surpassed other strongly-coupled systems in terms of coherence\cite{forn2019ultrastrong}. 
Moreover, SAAs do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strong with the free-propagating EM-waves in the on-chip 1D waveguides\cite{astafiev2010resonance} without having to use cavities at all. The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is already in the ultra-strong coupling regime.

A quantum system exposed to external driving can experience a number of quantum phenomena due to the resonant transitions between energy levels. The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (AT) splitting\cite{autler1955stark} which can happen in systems with just three energy levels. 
The main attention in our work is paid to the last effect, which related to the dressed states.
The AT effect has been studied in atomic\cite{picque1976direct} and molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and superconducting qubits\cite{li2011decoherence, novikov2013autler}.
